---
title: "index"
author: "Cynthia Cisneros"
date: "2022-08-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(ggplot2)
library(dplyr)
library(patchwork)
```

```{r, include = FALSE}
#This code chunk allows us to source the code from analysis
source("analysis.R", local = knitr::knit_global())
```
Below is a summary of all the information from the datasets that will be used

## Summary

```{r, echo = FALSE, message = FALSE}
#summary information
summary_info
```

## Bar Chart

```{r, echo = FALSE, message = FALSE}
#bar chart visual
plot(barchart)
```

Shows a bar chart of total jail population throughout the years of Urban Cities (side by side).

## Scatter Plot

```{r, echo = FALSE, message = FALSE}
#scatter plot visual
plot(scatterplot)
```

Shows a scatter plot of jail populations across each region and shows larger jail population in Northeast

## Map

```{r, echo = FALSE, message = FALSE}
#map visual
plot(map)
```

Blue and red map of non black and non white populations in jail. Red is the high and blue is the low, so in most states there is a low number of other races in jail compared to the rest.
